---
title: "Multi-area Grid Metrics Analyzer Comparison Plots"
author: "Created by: `r Sys.info()['user']`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document: 
    css: custom.css
    toc: yes
---

```{r setOptions, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set up default options for chunks, turn off error or warning messages.
knitr::opts_chunk$set(echo=FALSE, comment=NA, warning=FALSE, message=FALSE, include=TRUE,
                      fig.path=fig.path.name, dev='png', fig.width=12)

# Set dynamic height for figures
if (exists('zone.names')) { z.height = ( length(zone.names[!zone.names%in%ignore.zones]) %/% 3 + 
                                           length(zone.names[!zone.names%in%ignore.zones]) %% 3 ) * 4
  } else { z.height = 5 }
if (exists('region.names')) { r.height = ( length(region.names[!region.names%in%ignore.regions]) %/% 3 + 
                                             length(region.names[!region.names%in%ignore.regions]) %% 3 ) * 4
  } else {r.height = 4 }
if (exists('region.names')) { r.height2 = ( length(region.names[!region.names%in%ignore.regions]) %/% 3 + 
                                             length(region.names[!region.names%in%ignore.regions]) %% 3 ) * 3
  } else {r.height2 = 3 }
if (exists('reserve.names')) { res.height = ( length(reserve.names) %/% 3 + length(reserve.names) %% 3 ) * 5
  } else { res.height = 5 }
if (exists('reserve.names')) { res.height2 = ( length(reserve.names) %/% 3 + length(reserve.names) %% 3 ) * 3
  } else { res.height2 = 3 }
if (exists('interfaces')) { 
    i.height = ifelse(typeof(interfaces)=='character', 5, ( length(interfaces) ) * 5)
  } else { i.height = 5 }
if (exists('lines')) {
    l.height = ifelse(typeof(lines)=='character', 5, ( length(lines) ) * 5)
  } else { l.height = 5 }
s.height = ( length(db.loc) ) * 4
s.width = ( length(db.loc) %/% 3 + length(db.loc) %% 3 ) * 10
p.height = ( length(period.names) %/% 2 + length(period.names) %% 2 ) * 5
t.height = ( length(re.types) ) * 4
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### Data below generated for:
"`r gsub('.*Model', 'Model', db$filename)`"

***
## Annual Dispatch Stacks 
***
## 1. Total Generation
```{r total-gen-stack}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (total.gen.stack){
  if ( typeof(total.generation)=='character' ) {
    print('INPUT ERROR: total.generation has errors. Cannot run this section.')
  } else if ( typeof(total.avail.cap) == 'character' ) { 
    print('INPUT ERROR: total.avail.cap has errors. Cannot run this section.')
  } else{
    # Query annual generation by type.
    yr.gen = tryCatch( gen_by_type(total.generation, total.avail.cap), 
                       error = function(cond) { return('ERROR: gen_by_type function not returning correct results.') } )
    # Create plot
    plot.data = gen_stack_plot(yr.gen, load.data = r.load)
    print(plot.data[[1]] + theme(aspect.ratio = 2.5/length(db.loc),axis.text.x = element_text(angle = -30, hjust = 0)) +
          scale_y_continuous(breaks=plot.data[[2]], limits=c(min(plot.data[[2]]), max(plot.data[[2]])), 
                             expand=c(0,0), label=comma))
  }
} else { print('Section not run according to input file.')}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 1. Generation Differences
```{r gen-diff-stack}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_diff_gen_stack.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 2. Zonal Generation
```{r zone-gen-stacks, fig.width=10, fig.height=z.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (zone.gen.stacks) {
  if ( typeof(total.generation)=='character' ) {
    print('INPUT ERROR: total.generation has errors. Cannot run this section.')
  } else if ( typeof(total.avail.cap) == 'character' ) { 
    print('INPUT ERROR: total.avail.cap has errors. Cannot run this section.')
  } else{ 
    # Query region and zonal generation
    r.z.gen = tryCatch( region_zone_gen(total.generation, total.avail.cap), 
                        error = function(cond) { return('ERROR') } )  
    # Create plot
    plot.data = gen_stack_plot(r.z.gen[!Zone %in% ignore.zones, ],
                               load.data = z.load[!Zone %in% ignore.zones, ], 
                               filters = 'Zone', x_col='scenario')
    print(plot.data[[1]] + facet_wrap(~Zone, scales = 'free', ncol=3)+theme(aspect.ratio = 2.5, axis.text.x = element_text(angle = -30, hjust = 0)))
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 2. Zonal Generation Differences
```{r zone-gen-diff-stacks, fig.height=z.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_zone_gen_stacks.Rmd')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 3. Regional Generation
```{r region-gen-stacks, resize.height=T, fig.height=s.height, fig.width=12}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected run in the input file
if (region.gen.stacks) {
  if ( typeof(total.generation)=='character' ) {
    print('INPUT ERROR: total.generation has errors. Cannot run this section.')
  } else if ( typeof(total.avail.cap) == 'character' ) { 
    print('INPUT ERROR: total.avail.cap has errors. Cannot run this section.')
  } else{

    if( !exists('r.z.gen') ) {
      # Query region and zonal generation
      r.z.gen = tryCatch( region_zone_gen(total.generation, total.avail.cap), error = function(cond) { return('ERROR') } )
    }

    # Check if zonal.gen query worked and create plot of regional gen, else return an error.
    if ( typeof(r.z.gen)=='character' ) {
      print('ERROR: region_zone_gen function not returning correct results.')
    } else if ( typeof(r.load) == 'character' ) {
      print('ERROR: region_load function not returning correct results.')
    } else {
      if (length(unique(r.z.gen$Region))>length(unique(r.z.gen$Zone))) {
        region.load = r.load[!Region %in% ignore.regions, ] # Remove load data from regions being ignored
        
        setkey(region.load,Region)
        setkey(rz.unique,Region)
        region.load = rz.unique[region.load][!Zone %in% ignore.zones, ] # ignored regions removed above
        region.load = region.load[complete.cases(region.load),]
        plot.load = region.load

        x.col = 'Region'
        facet = facet_grid(scenario~., scales = 'free')
      } else{
        zone.load = z.load[!Zone %in% ignore.zones, ] # Remove load data from regions being ignored

        setkey(zone.load,Zone)
        setkey(rz.unique,Zone)
        zone.load = rz.unique[zone.load][!Region %in% ignore.regions, ] # ignored zones removed above
        zone.load = zone.load[complete.cases(zone.load),]
        plot.load = zone.load

        x.col = 'Zone'
        facet = facet_grid(scenario~., scales = 'free')
      }
      
      # Create and plot data
      p1 <- gen_stack_plot(r.z.gen[(!Zone %in% ignore.zones & !Region %in% ignore.regions),],
                           load.data = plot.load[(!Zone %in% ignore.zones & !Region %in% ignore.regions),],
                           filters = c('Region','Zone'), x_col = x.col)
      print(p1[[1]] + facet + theme(axis.text.x = element_text(angle = -30, hjust = 0)))
    }
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 3. Regional Generation Differences
```{r region-gen-diff-stacks, fig.height=r.height, fig.width=s.width}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_region_gen_stacks.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 4. Individual Regions
```{r individual-region-stacks, include=FALSE, fig.height=8}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if(individual.region.stacks.log) {
  if ( typeof(total.generation)=='character' | typeof(total.avail.cap) == 'character' |
       typeof(r.load) == 'character' ) {
    individual.region.stacks = 'INPUT ERROR: total.generation, total.avail.cap or r.load has errors. Cannot run this section.'
  } else { 
    # Query region and zonal generation
    r.z.gen = tryCatch( region_zone_gen(total.generation, total.avail.cap), 
                        error = function(cond) { return('ERROR') } )
    # If the regional query didn't work, return an error. Else create the plots by calling the markdown file.
    if ( typeof(r.z.gen)=='character' ) {
      print('ERROR: region_zone_gen function not returning correct results.')
    } else {
      # Select only those regions not excluded, or not in excluded zones
      plot.regions = region.names[!region.names %in% c(ignore.regions, rz.unique[Zone %in% ignore.zones, Region])]
      key.plots = lapply(plot.regions, function(r){
                         knit_expand(file = 'source_scripts/p_individual_region_stacks.Rmd', region.name=r)
                         })
      # Reconstruct the plot data into a format that will be output into the HTML below
      individual.region.stacks = knit_child(text = unlist(key.plots))
      }
    }
} else { individual.region.stacks = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r individual.region.stacks`


***
## 5-7. Specified Period Dispatch Stacks
``` {r key-period-dispatch, cache=FALSE, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (key.period.dispatch.total.log | key.period.dispatch.zone.log | key.period.dispatch.region.log){  
  if (length(period.names)>0) {

    # Call interval_gen function and proces data for plots
    source('source_scripts/d_key_period_dispatch.R')

    # As long as the file exists (previous source found the R script) this loop runs
    if ( exists('key.period.gen') ) {
    # Check to see if the right data is ready for plotting.
      if ( typeof(key.period.gen)=='character' ) {
        key.period.dispatch.total  = 'ERROR: interval_gen function not returning correct results.'
        key.period.dispatch.zone   = 'ERROR: interval_gen function not returning correct results.'
        key.period.dispatch.region = 'ERROR: interval_gen function not returning correct results.'
      } else {
        # Create data if total database info was selected in input file.
        if (key.period.dispatch.total.log) {
          key.plots.total = lapply(period.names, function(p){
            knit_expand(file = 'source_scripts/compare/c_p_key_period_dispatch_total.Rmd', period.name = p)
            })
          key.period.dispatch.total = knit_child(text = unlist(key.plots.total))
        } else {key.period.dispatch.total  = 'Section not run according to input file.'}
          
        # Create data if zonal dispatch stacks were selected in input file.
        if (key.period.dispatch.zone.log) {
            plot.zones = zone.names[!zone.names %in% ignore.zones]
            key.plots.zone = mapply(function(p,z){knit_expand(file = 'source_scripts/compare/c_p_key_period_dispatch_zone.Rmd', 
                                                              period.name = p, zone.name = z)},
                                    rep(period.names,length(plot.zones)), rep(plot.zones,each=n.periods))
          key.period.dispatch.zone = knit_child(text = unlist(key.plots.zone))
        } else {key.period.dispatch.zone   = 'Section not run according to input file.'}
          
        # Create data if regional dispatch stacks were selected in input file.
        if (key.period.dispatch.region.log) {
          plot.regions = region.names[!region.names %in% ignore.regions]
          key.plots.region = mapply(function(p,r){knit_expand(file = 'source_scripts/compare/c_p_key_period_dispatch_region.Rmd', 
                                                              period.name = p, region.name = r)},
                                    rep(period.names,length(plot.regions)), rep(plot.regions,each=n.periods))
          key.period.dispatch.region = knit_child(text = unlist(key.plots.region))
        } else {key.period.dispatch.region = 'Section not run according to input file.'}        
      }
    } else { key.period.dispatch.total  = 'Problem sourcing or running d_key_period_dispatch.R.'
             key.period.dispatch.zone   = 'Problem sourcing or running d_key_period_dispatch.R.'
             key.period.dispatch.region = 'Problem sourcing or running d_key_period_dispatch.R.' }
  } else { key.period.dispatch.total  = 'You didnt specify key periods. Cannot run this section.'
           key.period.dispatch.zone   = 'You didnt specify key periods. Cannot run this section.' 
           key.period.dispatch.region = 'You didnt specify key periods. Cannot run this section.' }
} else { key.period.dispatch.total  = 'Section not run according to input file.'
         key.period.dispatch.zone   = 'Section not run according to input file.' 
         key.period.dispatch.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### 5. Total
`r key.period.dispatch.total`

***
### 6. Zones
`r key.period.dispatch.zone`

***
### 7. Regions
`r key.period.dispatch.region`

***
## 8-11. Curtailment
***
### 8. Average Daily Curtailment
```{r yearly-curtailment}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_daily_curtailment.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 9. Average Daily Curtailment by Type
```{r yearly-curtailment-by-type, fig.height=t.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_daily_curtailment_type.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 10. Average Interval Curtailment
```{r daily-curtailment}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_interval_curtailment.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 11. Average Interval Curtailment by Type
```{r daily-curtailment-by-type, fig.height=t.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_interval_curtailment_type.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 12. Total Gen
```{r annual-generation-table, fig.width=10}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (annual.generation.table){
  if ( typeof(total.generation)=='character' | typeof(total.avail.cap) == 'character' ) {
    print('INPUT ERROR: total.generation or total.avail.cap has errors. Cannot run this section.')
  } else {
    # Run the query function.
    yr.gen = tryCatch(gen_by_type(total.generation, total.avail.cap), 
                        error = function(cond) { return('ERROR: gen_by_type function not returning correct results') } ) 
    # Set the order level that generatino type will be displayed.
    yr.gen[, Type := factor(Type, levels = c(gen.order))] 
    setorder(yr.gen,Type)
    
    # Separate out curtailment from generation
    curt = yr.gen[Type=='Curtailment', ]
    yr.gen = yr.gen[Type!='Curtailment', ]
    
    # Calculate the percent generation of each type, and percent curtailment
    yr.gen[, Total:=sum(GWh), by=.(scenario)]
    yr.gen[, Percent:=GWh/Total*100]
    yr.gen[, Total:=NULL]
    curt[, Total:=GWh+yr.gen[Type %in% re.types, sum(GWh)] ]
    curt[, Percent:=GWh/Total*100]
    curt[, Total:=NULL]
    
    # combine back into one table. 
    yr.gen = rbindlist(list(yr.gen, yr.gen[,.(Type='Total',GWh=sum(GWh),Percent=sum(Percent)), by=.(scenario)], curt))
    row.names(yr.gen) = NULL
    kable(yr.gen, format.args = list(big.mark = ','), digits=2) 
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 13. Total Curtailment (GWh)
```{r annual-curtailment-table, fig.width=12}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (annual.curtailment.table){
  if ( typeof(total.generation)=='character' | typeof(total.avail.cap) == 'character' ) {
    print('INPUT ERROR: total.generation or total.avail.cap has errors. Cannot run this section.')
  } else {
    # Run the query function.
    yr.curt = tryCatch(curt_by_type(total.generation, total.avail.cap), 
                        error = function(cond) { return('ERROR: gen_by_type function not returning correct results') } ) 
    # Set the order level that generatino type will be displayed.
    yr.curt[, Type := factor(Type, levels = c(gen.order))] 
    setorder(yr.curt,Type)

    # Calculate the percent curtailed of each type
    yr.curt[, Percent:=Curtailment/`Available Energy`*100]
    yr.curt = rbindlist(list(yr.curt, yr.curt[,.(Type='Total',`Available Energy`=sum(`Available Energy`),
                                                 Generation=sum(Generation), Curtailment=sum(Curtailment),
                                                 Percent=sum(Curtailment)/sum(`Available Energy`)*100), by=.(scenario)]))
    row.names(yr.curt) = NULL
    setnames(yr.curt,'Percent','Percent Curtailed, %')
    kable(yr.curt, format.args = list(big.mark = ','), digits=2) 
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 28. Total Curtailment Difference
```{r yearly-curtailment-diff}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (curtailment.diff.table) {
  if ( typeof(total.generation)=='character' ) {
    print('ERROR: total.generation has errors. Cannot run this section.')
  } else if ( typeof(total.avail.cap) == 'character' ) { 
    print('ERROR: total.avail.cap has errors. Cannot run this section.')
  } else{
    # Run the cost query function
    curt.diff = tryCatch( curtailment_diff(total.generation, total.avail.cap), 
                          error = function(cond) { return('ERROR: curtailment diff function not returning correct results.') })
    kable(curt.diff, format.args = list(big.mark = ','), digits=2)
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 14. Total Costs
```{r annual-cost-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (annual.cost.table) {
  if ( typeof(total.emissions.cost)=='character' & typeof(total.fuel.cost)=='character' & 
       typeof(total.ss.cost)=='character' & typeof(total.vom.cost)=='character' ) {
    print('INPUT ERROR: all of total.emissions cost, total.fuel.cost, 
           total.ss.cost, and total.vom.cost has errors. Cannot run this section.')
  } else{
    # Run the cost query function
    cost.table = tryCatch( costs(total.emissions.cost, total.fuel.cost, total.ss.cost, total.vom.cost), 
                           error = function(cond) { return('ERROR: costs function not returning correct results.') })
    kable(cost.table, format.args = list(big.mark = ','))
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 10. Total Cost Differences
```{r annual-cost-difference-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (annual.cost.table) {
  # Run the cost query function
  cost.diff.table = tryCatch( costs_diff(total.emissions.cost, total.fuel.cost, total.ss.cost, total.vom.cost), 
                              error = function(cond) { return('ERROR: costs function not returning correct results.') })
  kable(cost.diff.table, format.args = list(big.mark = ',')) 
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 15. Region and Zone Info (GWh)
``` {r region-flow-tables, results = 'asis'}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (region.zone.flow.table) {
  if ( typeof(total.region.load)=='character' | typeof(total.region.imports)=='character' | 
       typeof(total.region.exports)=='character' | typeof(total.region.ue)=='character' ) {
    print('INPUT ERROR: at least one of total.region.load, total.region.imports, 
           total.region.exports, or total.region.ue has errors. Cannot run this section.')
  } else{
    # Query region and zone stats.
    r.stats = tryCatch( region_stats(total.region.load, total.region.imports, total.region.exports, total.region.ue), 
                        error = function(cond) { return('ERROR: region_stats function not returning correct results.') })
      # Set names if data exists
    if ( !typeof(r.stats)=='character' ) { 
      setnames(r.stats, 'name', 'Region Name')
    } else{ print("ERROR: region_stats not returning correct results")}
    # Print data. Will print error message if errors
    kable(r.stats[!`Region Name` %in% ignore.regions, ], format.args = list(big.mark = ','), digits=2)
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

``` {r zone-flow-tables, results = 'asis'}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (region.zone.flow.table) {
  if ( (typeof(total.region.load)=='character' | typeof(total.region.imports)=='character' | 
         typeof(total.region.exports)=='character' | typeof(total.region.ue)=='character') & 
       (typeof(total.zone.load)=='character' | typeof(total.zone.imports)=='character' | 
               typeof(total.zone.exports)=='character' | typeof(total.zone.ue)=='character') ) {
    print('INPUT ERROR: at least one of total.region.load, total.region.imports, 
           total.region.exports, or total.region.ue, or total.zone.load, total.zone.imports, 
           total.zone.exports, or total.zone.ue has errors. Cannot run this section.')
  } else{
    # Query region and zone stats.
    z.stats = tryCatch( zone_stats(total.region.load, total.region.imports, total.region.exports, total.region.ue, 
                                   total.zone.load, total.zone.imports, total.zone.exports, total.zone.ue), 
                        error = function(cond) { return('ERROR: zone_stats function not returning correct results.') })
    # Set names if data exists
    if ( !typeof(z.stats)=='character' ) { 
      setnames(z.stats, 'name', 'Zone Name')
    } else{ print("ERROR: region_stats not returning correct results")}
    # Print data. Will print error message if errors
    kable(z.stats[!`Zone Name` %in% ignore.zones], format.args = list(big.mark = ','), digits=2)
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 12. Region and Zone Differences (GWh)
``` {r region-zone-flow-diff-tables}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 if (region.zone.flow.table) {
  if ( (typeof(total.region.load)=='character' | typeof(total.region.imports)=='character' | 
         typeof(total.region.exports)=='character' | typeof(total.region.ue)=='character') & 
       (typeof(total.zone.load)=='character' | typeof(total.zone.imports)=='character' | 
               typeof(total.zone.exports)=='character' | typeof(total.zone.ue)=='character') ) {
    print('INPUT ERROR: at least one of total.region.load, total.region.imports, 
           total.region.exports, or total.region.ue, or total.zone.load, total.zone.imports, 
           total.zone.exports, or total.zone.ue has errors. Cannot run this section.')
  } else{
    # Query region and zone stats.
    z.stats = tryCatch( zone_stats(total.region.load, total.region.imports, total.region.exports, total.region.ue, 
                                   total.zone.load, total.zone.imports, total.zone.exports, total.zone.ue), 
                        error = function(cond) { return('ERROR: zone_stats function not returning correct results.') })
    # Set names if data exists
    if ( !typeof(z.stats)=='character' ) { 
      z.diff.stats = z.stats[,.(scenario, Exports=Exports-Exports[scenario==ref.scenario],
                                Imports=Imports-Imports[scenario==ref.scenario],
                                Load=Load-Load[scenario==ref.scenario],
                                `Unserved Energy`=`Unserved Energy`-`Unserved Energy`[scenario==ref.scenario]), 
                             by=.(name)]
      setnames(z.diff.stats, 'name', 'Zone Name')
      z.diff.stats=z.diff.stats[scenario!=ref.scenario]
    } else{ print("ERROR: region_stats not returning correct results")}
    # Print data. Will print error message if errors
    kable(z.diff.stats[!`Zone Name` %in% ignore.zones], format.args = list(big.mark = ','), digits=2)
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 16. Interface Flow Table
```{r interface-flow-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if(interface.flow.table) {
  if (length(interfaces)>0) {
    if (typeof(total.interface.flow)=='character'){
      print('INPUT ERROR: total.interface.flow has errors. Cannot run this section')
    } else{
      # Call the query function to get interface flows for the interfaces selected in the input file.
      interface.flows = tryCatch( annual_interface_flows(total.interface.flow), 
                                  error=function(cond) {return('ERROR: interface_flows query not returning correct results.')})
      # Print data 
      kable(interface.flows, digits=3)
    }
  } else { print('No interfaces specified. No interface data will be shown.')}
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 17. Interface Flow Plots
```{r interface-flow-plots, resize.width=T, fig.width=10, fig.height=i.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (interface.flow.plots) {
  if (length(interfaces)>0) {
    if ( typeof(interval.interface.flow) == 'character' ) {
      print('INPUT ERROR: interval.interface.flow not correct. Cannot run this section')
    } else { 
      # Call the query function to get interface flows for the interfaces selected in the query function.
      interface.flows = tryCatch( interval_interface_flows(interval.interface.flow), 
                                  error=function(cond) {return('ERROR: interface_flows query not returning correct results.')})
        
      # Check for errors in the query function. If theres an error don't continue.
      if ( typeof(interface.flows)=='character' ) { 
        print('ERROR: interface_flows function not returning correct results.')
      } else {
        # change name to interface in order to not hit recursive error
        interface.flows[, interface:=factor(name, levels = interfaces)]
        # Add day and interval
        interface.flows[, day := as.POSIXlt(time)[[8]] ]
        interface.flows[, interval := 1:intervals.per.day, by=.(day,scenario)]
        # Get interval plots
        avg.interface = interface.flows[, .(value=sum(value)),by=.(scenario,interface,interval)]
        avg.interface[, hour := floor((interval-1)*(3600*24/intervals.per.day)/3600)]
        avg.interface[, minute := floor((interval-1)*(3600*24/intervals.per.day)/60-hour*60)]
        avg.interface[, second := floor((interval-1)*(3600*24/intervals.per.day)-hour*3600-minute*60)]
        avg.interface[, time := as.POSIXct(paste(hour,minute,second, sep=":"),format="%H:%M:%S",tz='UTC')]
      
        p1 = interface_plot(avg.interface, x_col = 'time', color='scenario')
        print(p1 + labs(title='Interval Flow') + facet_wrap(~interface,ncol=1,scales='free') +
                scale_x_datetime(breaks = date_breaks(width = "2 hour"), labels = date_format("%H:%M"), 
                                 expand = c(0, 0), timezone='UTC'))
        # Aggregate interval flow data into daily flow data
        daily.flows = interface.flows[, .(value=sum(value)), by=.(day,name,scenario)]
        daily.flows[,time:=as.POSIXct(as.character(day+1),format="%j")]
        p2 = interface_plot(daily.flows, x_col = 'time', color='scenario')
        if (nrow(daily.flows) > 30*length(interfaces)){
          p2 = p2 + scale_x_datetime(breaks=date_breaks(width="1 month"), 
                     labels = date_format("%b"), expand = c(0, 0), timezone='UTC')
        }
        print(p2 + labs(title='Daily Flow') + facet_wrap(~name,ncol=1,scales='free'))
      }
    }
  } else { print('No interfaces specified. No interface data will be shown.')}
} else { print('Section not run according to input file.') }

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 18. Specified Period Interface Flow Plot
```{r key-period-interface-flow-plots, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (key.period.interface.flow.plots) {
  if (length(interfaces)>0) {
    if (length(period.names)>0) {

      # Pull out interface flow data for only specified periods in input file
      source('source_scripts/d_key_period_interface_flow.R')
      
      # As long as the file exists (previous source found the R script) this loop runs
      if ( exists('plot.flows') ) {
        # Check to see if the right data is ready for plotting.
        if ( typeof(plot.flows)=='character' ) {
          print('ERROR: interval_interface_flows function not returning correct results.')
        } else {        
          # Create data for each plot for the interesting periods
          figure.height = i.height
          key.plots = lapply(period.names, function(p){
                             knit_expand(file = 'source_scripts/compare/c_p_key_period_interface_flow.Rmd', period.name = p)
                             }) 
          # Reconstruct the plot data into a format that will be output into the HTML below
          key.period.interface.flow = knit_child(text = unlist(key.plots))
       
        }
      } else { key.period.interface.flow = 'Problem sourcing or running d_key_period_interface_flow.R.' }
    } else { key.period.interface.flow = 'You didnt specify key periods. Cannot run this section.'}
  } else { key.period.interface.flow = 'No interfaces specified. No interface data will be shown.'}
} else { key.period.interface.flow = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r key.period.interface.flow`

***
## 33. Line Flow Table
```{r line-flow-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if(line.flow.table) {
  if (length(lines)>0) {
    if (typeof(total.line.flow)=='character'){
      print('INPUT ERROR: total.line.flow has errors. Cannot run this section')
    } else{
      # Call the query function to get line flows for the lines selected in the input file.
      line.flows = tryCatch( annual_line_flows(total.line.flow), 
                             error=function(cond) {return('ERROR: line_flows query not returning correct results.')})
      # Print data 
      kable(line.flows, digits=3)
    }
  } else { print('No lines specified. No line data will be shown.')}
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 34. Line Flow Plots
```{r line-flow-plots, resize.width=T, fig.width=10, fig.height=l.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (line.flow.plots) {
  if (length(lines)>0) {
    if ( typeof(interval.line.flow) == 'character' ) {
      print('INPUT ERROR: interval.line.flow not correct. Cannot run this section')
    } else { 
      # Call the query function to get line flows for the lines selected in the query function.
      line.flows = tryCatch( interval_line_flows(interval.line.flow), 
                             error=function(cond) {return('ERROR: line_flows query not returning correct results.')})
      
      # Check for errors in the query function. If theres an error don't continue.
      if ( typeof(line.flows)=='character' ) { 
        print('ERROR: line_flows function not returning correct results.')
      } else {
        # change name to line in order to not hit recursive error
        line.flows[, line:=factor(name, levels = lines)]
        # Add day and interval
        line.flows[, day := as.POSIXlt(time)[[8]] ]
        line.flows[, interval := 1:intervals.per.day, by=.(day,scenario)]
        # Get interval plots
        avg.line = line.flows[, .(value=sum(value)),by=.(scenario,line,interval)]
        avg.line[, hour := floor((interval-1)*(3600*24/intervals.per.day)/3600)]
        avg.line[, minute := floor((interval-1)*(3600*24/intervals.per.day)/60-hour*60)]
        avg.line[, second := floor((interval-1)*(3600*24/intervals.per.day)-hour*3600-minute*60)]
        avg.line[, time := as.POSIXct(paste(hour,minute,second, sep=":"),format="%H:%M:%S",tz='UTC')]

        p1 = interface_plot(avg.line, x_col = 'time', color='scenario')
        print(p1 + labs(title='Interval Flow') + facet_wrap(~line,ncol=1,scales='free') +
                scale_x_datetime(breaks = date_breaks(width = "2 hour"), labels = date_format("%H:%M"), expand = c(0, 0)))
        # Aggregate interval flow data into daily flow data
        daily.flows = line.flows[, .(value=sum(value)), by=.(day,name,scenario)]
        daily.flows[,time:=as.POSIXct(as.character(day+1),format="%j")]
        p2 = interface_plot(daily.flows, x_col = 'time', color='scenario')
        if (nrow(daily.flows) > 30*length(lines)){
          p2 = p2 + scale_x_datetime(breaks=date_breaks(width="1 month"), 
                                     labels = date_format("%b"), expand = c(0, 0))
        }
        print(p2 + labs(title='Daily Flow') + facet_wrap(~name,ncol=1,scales='free'))
      }
    }
  } else { print('No lines specified. No line data will be shown.')}
} else { print('Section not run according to input file.') }

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 35. Specified Period Line Flow Plot
```{r key-period-line-flow-plots, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (key.period.line.flow.plots) {
  if (length(lines)>0) {
    if (length(period.names)>0) {
      
      # Pull out line flow data for only specified periods in input file
      source('source_scripts/d_key_period_line_flow.R')
      
      # As long as the file exists (previous source found the R script) this loop runs
      if ( exists('plot.flows') ) {
        # Check to see if the right data is ready for plotting.
        if ( typeof(plot.flows)=='character' ) {
          print('ERROR: interval_line_flows function not returning correct results.')
        } else {        
          # Create data for each plot for the interesting periods
          figure.height = l.height
          key.plots = lapply(period.names, function(p){
            knit_expand(file = 'source_scripts/compare/c_p_key_period_interface_flow.Rmd', period.name = p)
          }) 
          # Reconstruct the plot data into a format that will be output into the HTML below
          key.period.line.flow = knit_child(text = unlist(key.plots))
          
        }
      } else { key.period.line.flow = 'Problem sourcing or running d_key_period_line_flow.R.' }
    } else { key.period.line.flow = 'You didnt specify key periods. Cannot run this section.'}
  } else { key.period.line.flow = 'No lines specified. No line data will be shown.'}
} else { key.period.line.flow = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r key.period.line.flow`


***
## 19-21. Reserves
***
### 19. Annual Reserve Provisions and Shortage
```{r annual-reserves-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if(annual.reserves.table) {
  if (typeof(total.reserve.provision)=='character' | typeof(total.reserve.shortage)=='character'){
    print('INPUT ERROR: total.reserve.provision or total.reserve.shortage has errors. Cannot run this section')
  } else{
    # Call the query function to get annual reserve amounts.
    annual.reserves = tryCatch( annual_reserves(total.reserve.provision, total.reserve.shortage), 
                                error = function(cond) { return('ERROR: annual_reserves function not returning correct results.') })
    if(typeof(annual.reserves)!='character') { 
      if(length(unique(annual.reserves$scenario))>1){
        kable(annual.reserves[, .(Type, scenario, `Provisions (GWh)`, `Shortage (GWh)`)], format.args = list(big.mark = ',')) 
      } else{
        kable(annual.reserves[, .(Type, `Provisions (GWh)`, `Shortage (GWh)`)], format.args = list(big.mark = ',')) 
      }
    } else { print('ERROR: annual_reserves is not returning correct results.')}
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 20. Average Interval and Daily Reserve Provisions
```{r reserves-plots}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if(reserves.plots) {
  if (typeof(interval.reserve.provision)=='character'){
      print('INPUT ERROR: interval.reserve.provision has errors. Cannot run this section')
    } else{
    # Reserves interval data query
    r = tryCatch( interval_reserves(interval.reserve.provision), error = function(cond) { return('ERROR') })
    
    if ( typeof(r)=='character' ) { 
      print('ERROR: interval_reserves function not returning correct results.')
    } else {
      
      # Average reserve provision at each interval
      int.avg = r[, .(Provision = mean(provision)/1000), by = .(interval,scenario)]
      int.avg[, hour := floor((interval-1)*(3600*24/intervals.per.day)/3600)]
      int.avg[, minute := floor(((interval-1)*(3600*24/intervals.per.day)/3600-hour)/60)]
      int.avg[, second := floor((((interval-1)*(3600*24/intervals.per.day)/3600-hour)/60-minute)/60)]
      int.avg[, time := as.POSIXct(paste(hour,minute,second, sep=":"),'UTC',format="%H:%M:%S")]
    
      # Creating interval reserves provisions plot
      p.1 = line_plot(int.avg, c('interval','scenario'),'time', 'Provision', 'Reserve Provision (GWh)',color='scenario')
      p.1 = p.1 + scale_x_datetime(breaks = date_breaks(width = "2 hour"), 
                                   labels = date_format("%H:%M"), expand = c(0, 0), timezone='UTC')
    
      # Calculating the daily hourly average
      dy.avg = r[, .(Provision = mean(provision)/1000), by = .(day,scenario)]
      dy.avg[, time := as.POSIXct(as.character(day+1),format='%j')]
    
      # Creating average daily reserves provisions plot
      p.2 = line_plot(dy.avg, c('day','scenario'),'time', 'Provision', 'Reserve Provision (GWh)',color='scenario')
      if (nrow(dy.avg) > 30) {
        p.2 = p.2 + scale_x_datetime(breaks = date_breaks(width = "1 month"), 
                                     labels = date_format("%b %d"), expand = c(0, 0), timezone='UTC')
      }
      print(p.1)
      print(p.2)
    }
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 21. Reserve Provisions by generator type
```{r reserves-stacks, fig.height=res.height, fig.width=10}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if(reserve.stack) {
  if (typeof(total.gen.res)=='character'){
      print('INPUT ERROR: total.gen.res has errors. Cannot run this section')
    } else{
    # Query annual reserves provision by type.
    yr.res.scen = tryCatch( annual_reserves_provision(total.gen.res), error = function(cond) { return('ERROR') })
    
    if ( typeof(yr.res.scen)=='character' ) { 
      print('ERROR: annual_reserves_provision function not returning correct results.')
    } else {
      # Create plot
      plot.data = gen_stack_plot(yr.res.scen, filters = c('Reserve','scenario'))
      print(plot.data[[1]] + facet_wrap(~Reserve,ncol=3,scales='free') + 
              theme(axis.text.x = element_text(angle = -30, hjust = 0)))
    }
  }
} else { print('Section not run according to input file.') }

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 27. Annual Reserve Shortage by Scenario
```{r annual-reserves-scen-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (annual.res.short.table) {
  # Run the cost query function
  res.short.table = tryCatch( annual_reserves_short(total.reserve.provision, total.reserve.shortage), 
                              error = function(cond) { return('ERROR: reserve function not returning correct results.') })
  kable(res.short.table, format.args = list(big.mark = ','))
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 22. Region and Zone Generation (GWh)
```{r region-gen-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (region.zone.gen.table) {
  if (typeof(r.load)=='character' | typeof(total.generation)=='character' | 
      typeof(total.avail.cap)=='character' ) {
    print('INPUT ERROR: r.load, total.generation, or total.avail.cap not correct. Cannot run this section.')
  } else{
    r.z.gen = tryCatch( region_zone_gen(total.generation, total.avail.cap), 
                        error = function(cond) { return('ERROR: region_zone_gen function not returning correct results.') } )
    if ( typeof(r.z.gen)=='character' ) { 
      r.gen.table = 'ERROR: region_zone_gen function not returning correct results.'
    } else {
      r.z.gen[, Type := factor(Type, levels = gen.order)] # Reassign the order which the generation type will be displayed.
      
      # Sum regional generation by type
      r.gen.table = r.z.gen[!Region %in% ignore.regions, .(GWh = sum(GWh)), by=.(Region, Type, scenario)] %>%
        dcast.data.table(Region+scenario~Type, value.var = 'GWh')
      r.gen.table[is.na(r.gen.table)] = 0
      region.load = r.load[!Region %in% ignore.regions, .(Region, scenario, Load = value)]
      setkey(region.load,Region,scenario)
      setkey(r.gen.table,Region,scenario)
      r.gen.table = r.gen.table[region.load]
    }
    # Print results
    kable(r.gen.table, digits=2, format.args = list(big.mark = ','))
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
```{r zone-gen-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (region.zone.gen.table) {
  if (typeof(z.load)=='character' | typeof(total.generation)=='character' | 
      typeof(total.avail.cap)=='character' ) {
    print('INPUT ERROR: z.load, total.generation, or total.avail.cap not correct. Cannot run this section.')
  } else{
    r.z.gen = tryCatch( region_zone_gen(total.generation, total.avail.cap), 
                        error = function(cond) { return('ERROR: region_zone_gen function not returning correct results.') } )
    if ( typeof(r.z.gen)=='character' ) { 
      z.gen.table = 'ERROR: region_zone_gen function not returning correct results.'
    } else {
      r.z.gen[, Type := factor(Type, levels = gen.order)] # Reassign the order which the generation type will be displayed.
      
      # Sum zonal generation by type
      z.gen.table = r.z.gen[!Zone %in% ignore.zones, .(GWh = sum(GWh)), by=.(Zone, Type, scenario)] %>%
        dcast.data.table(Zone+scenario~Type, value.var = 'GWh')
      z.gen.table[is.na(z.gen.table)] = 0
      zone.load = z.load[!Zone %in% ignore.zones, .(Zone, scenario, Load = value)]
      setkey(zone.load,Zone,scenario)
      setkey(z.gen.table,Zone,scenario)
      z.gen.table = z.gen.table[zone.load]
    }
    # Print results
    kable(z.gen.table, digits=2, format.args = list(big.mark = ','))
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 23. Capacity Factors
```{r capacity-factor-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if(capacity.factor.table) {
  if ( typeof(total.generation)=='character' | typeof(total.installed.cap) == 'character' ) {
    print('INPUT ERROR: total.generation or total.installed.cap has errors. Cannot run this section.')
  } else{
    # Call the query function to get capacity factor.
    cf = tryCatch( capacity_factor(total.generation, total.installed.cap), 
                   error = function(cond) { return('ERROR: capacity_factor function not returning correct results.') })
    if(length(unique(cf$scenario))>1){
        kable(cf, format.args = list(big.mark = ','), digits=2)
      } else{
        kable(cf[, .(Type, `MaxCap (GWh)`, `Gen (GWh)`, `Capacity Factor (%)`)], format.args = list(big.mark = ',')) 
      }
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 24. Region Price Duration Curves
```{r price-duration-curve, fig.width = 15, fig.height=r.height2}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_price_duration_curve.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 24. Reserve Price Duration Curves
```{r res-price-duration-curve, fig.width = 15, fig.height=res.height2}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_res_price_duration_curve.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 25-26. DA-RT Committment and Dispatch Plots
```{r committment-dispatch, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (commit.dispatch.region | commit.dispatch.zone) {
  if (length(da.rt.types)>0) {
    source('source_scripts/d_DA_RT_commit_dispatch.R') # Call this R script which created the data needed for plotting.
  
    # As long as the file exists (previous source found the R script) this loop runs
    if ( exists('plot.data.all') ) {
      # Check to see if the right data is ready for plotting.
      if ( typeof(plot.data.all)=='character' ) {
        print('ERROR: cap_committed function not returning correct results.')
      } else {
        # Check if zonal DA-RT plots were selected in input file. If so create a plot for each zone
        if (commit.dispatch.zone) {
          plot.zones = zone.names[!zone.names %in% ignore.zones]
          da.rt.zone = mapply(function(p,z){knit_expand(file = 'source_scripts/compare/c_p_DA_RT_commit_dispatch_zone.Rmd', 
                                                        period.name = p, zone.name = z)},
                              rep(period.names,length(plot.zones)), rep(plot.zones,each=n.periods))
          da.rt.zone = knit_child(text = unlist(da.rt.zone))
        } else {da.rt.zone = 'Section not run according to input file.'}
        
        # Check if regional DA-RT plots were selected in input file. If so create a plot for each region
        if (commit.dispatch.region) {  
          plot.regions = region.names[!region.names %in% ignore.regions]
          da.rt.region = mapply(function(p,r){knit_expand(file = 'source_scripts/compare/c_p_DA_RT_commit_dispatch_region.Rmd', 
                                                          period.name = p, region.name = r)},
                                rep(period.names,length(plot.regions)), rep(plot.regions,each=n.periods))
          da.rt.region = knit_child(text = unlist(da.rt.region))
        } else {da.rt.region = 'Section not run according to input file.'} 
      }
    } else if ( typeof(interval.da.committment) == 'character' ) { 
        da.rt.zone = 'INPUT ERROR: interval.da.committment has errors. Cannot run this section.'
      da.rt.region = 'INPUT ERROR: interval.da.committment has errors. Cannot run this section.'
    } else if ( typeof(interval.avail.cap) == 'character' ) { 
        da.rt.zone = 'INPUT ERROR: interval.avail.cap has errors. Cannot run this section.'
      da.rt.region = 'INPUT ERROR: interval.da.committment has errors. Cannot run this section.'
    } else {   da.rt.zone = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'
             da.rt.region = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.' }
  } else {   da.rt.zone = 'You didnt specify generation types for DA-RT plots. Plots cannot be created.'
           da.rt.region = 'You didnt specify generation types for DA-RT plots. Plots cannot be created.' }
} else {   da.rt.zone = 'Section not run according to input file.'
         da.rt.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### 25. Zones
`r da.rt.zone`

### 26. Regions
`r da.rt.region`

***
## 33. Revenue by Generator Type
```{r revenue-plots, fig.width = 12, fig.height=r.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_revenue.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

## 22. Generation comparison by Generator Type
```{r generation-comparison, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (compare.dispatch.region | compare.dispatch.zone) {
  if (length(da.rt.types)>0){
    source('source_scripts/compare/c_d_gen_comparison.R') # Call this R script which created the data needed for plotting.
    
    # As long as the file exists (previous source found the R script) this loop runs
    if ( exists('compare.plot.data') ) {
      # Check to see if the right data is ready for plotting.
      if ( typeof(compare.plot.data)=='character' ) {
        print('ERROR: cap_committed function not returning correct results.')
      } else {
        
        # Check if zonal DA-RT plots were selected in input file. If so create a plot for each zone
        if (compare.dispatch.zone) {
          comp.gen.zone = mapply(function(t,z){ knit_expand(file = 'source_scripts/compare/c_p_key_period_gen_comparison_zone.Rmd', 
                                                            type.name = t, zone.name = z) },
                                 rep(da.rt.types,length(zone.names)), rep(zone.names,each=length(da.rt.types)))
          comp.gen.zone = knit_child(text = unlist(comp.gen.zone))
        } else {comp.gen.zone = 'Section not run according to input file.'}
        
        # Create a plot for each region.
        if (compare.dispatch.region) {  
          comp.gen.region = mapply(function(t,r){ knit_expand(file = 'source_scripts/compare/c_p_key_period_gen_comparison_region.Rmd', 
                                                              type.name = t, region.name = r) },
                                   rep(da.rt.types,length(region.names)), rep(region.names,each=length(da.rt.types)))
          comp.gen.region = knit_child(text = unlist(comp.gen.region))
        } else {comp.gen.region = 'Section not run according to input file.'}
      }
    } else { comp.gen.zone   = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'
             comp.gen.region = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'}
  }else {   comp.gen.zone = 'You didnt specify generation types for DA-RT plots. Plots cannot be created.'
          comp.gen.region = 'You didnt specify generation types for DA-RT plots. Plots cannot be created.' }
} else { comp.gen.zone   = 'Section not run according to input file.'
         comp.gen.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```


### Zones
`r comp.gen.zone`

***
### Regions
`r comp.gen.region`


***
## 30. Model Run Times
```{r model-run-times}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if(runtime.table) {
  if ( typeof(phase.runtime)=='character' ) {
    print('INPUT ERROR: phase.runtime has errors. Cannot run this section.')
  } else{
    if(length(unique(phase.runtime$scenario))>1){
        kable(dcast(phase.runtime,phase~scenario,value.var='time'), format.args = list(big.mark = ','), digits=2)
      } else{
        kable(phase.runtime, format.args = list(big.mark = ',')) 
      }
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```



***
## 36. Installed Capacity
```{r installed-capacity}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if(installed.cap.plot) {
  if ( typeof(total.installed.cap)=='character' ) {
    print('INPUT ERROR: total.installed.cap has errors. Cannot run this section.')
  } else{
    # Add type
    total.installed.cap[, Type:=gen.type.mapping[name] ]
    total.installed.cap[, GWh:=value] # Changing this so we can use gen_stack_plot
    # Create plot
    plot.data = gen_stack_plot(total.installed.cap)
    print(plot.data[[1]] + theme(aspect.ratio = 2.5/length(db.loc),axis.text.x = element_text(angle = -30, hjust = 0)) +
          scale_y_continuous(breaks=plot.data[[2]], limits=c(min(plot.data[[2]]), max(plot.data[[2]])), 
                             expand=c(0,0), label=comma) + 
            ylab("Installed Capacity, GW"))
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```


