```{r Gen-compare-region-{{region.name}}-{{type.name}}, results='asis', include=TRUE}
r.name = '{{region.name}}' # Assign region name
t.name = '{{type.name}}' # Assign generator type name
cat("### ", t.name, ': ', r.name) # Print period and region name above the plot
text.plot=16 # Plot text size.
figure.width = 15
figure.height = p.height
```

```{r Gen-compare-plot-region-{{region.name}}-{{type.name}}, fig.width=figure.width, fig.height=figure.height, include=TRUE}
# Check to make sure this region shouldn't be ignored.
if ( !r.name %in% ignore.regions ) {
  
  # Select data for specific type and region
  plot.data = compare.plot.data[Type==t.name & Region==r.name, .(GWh = sum(value)/1000), 
                            by=.(scenario, time, Region, Type, Period)]
  
  # this is just for scaling the y-axis 
  blank_data = plot.data[, .(ylim=GWh*1.06), by=.(scenario,time,Period)]
  
  # Check that there is actually generation data to plot, otherwise don't make a plot.
  if ( length(plot.data$GWh)>0 & sum(plot.data$GWh)>0 ) {
  
  # Plot data
  ggplot(plot.data,aes(time,GWh, color=scenario))+
    geom_line(size=1.2)+      
    geom_blank(data=blank_data, aes(x=time, y=ylim))+
    expand_limits(y=0)+
    scale_color_brewer(palette="Set1")+
    ylab("Generation (GW)")+xlab(NULL)+
    facet_wrap(~Period,ncol=2, scales="free_x")+
    theme(legend.key = element_rect(color = "grey70", size = 0.8), 
          legend.key.size = grid::unit(1.5, "lines"),  
          legend.text = element_text(size=text.plot),  text=element_text(size=text.plot), 
          strip.text=element_text(face=1, size=rel(0.8)), 
          axis.text.x=element_text(size=text.plot/1.2), 
          axis.title=element_text(size=text.plot, face=2),
          panel.grid.major = element_line(colour = "grey85"),
          panel.grid.minor = element_line(colour = "grey93"),
          panel.spacing = unit(0.45, "lines"))
  }
  
}